Hysteresis in human computation:\\ how one task affects another

### 2015-09-10 docs/publications/2015.04_PNAS/man.tex
fix table caption

\usepackage{xr}
\externaldocument[S]{supp}
\usepackage{dcolumn}
\usepackage{multirow}
\usepackage{booktabs}
\newcolumntype{d}{D{.}{.}{4.0}}
\newcolumntype{s}{D{.}{.}{1.4}}

@@

\dropcap{M}icrotask platforms are online marketplaces in which \textit{requesters} 
post batches of tasks, and \textit{workers} complete them
for remuneration, a sense of purpose, and fun
\cite{kazai2013analysis}.
Typical tasks include tagging and categorizing images,
%\cite{6116320,Zhai2012357}, 
coding and transcribing media,
%\cite{chandler2013breaking,Berinsky2012351,Finnerty2013},%paolacci2010running}, 
judging the relevancy or quality of content, 
and performing surveys for academic or market reserach purposes (see Table SX for a survey of task types).
%\cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.

@@

Our image-labeling tasks were performed on the MTurk microtask platform.  We
chose image labeling because it is very common,
%,paolacci2010running},
and because it is prototypical for any kind of task in which the worker is
asked to provide a response that is not precisely determined by the prompt, but
instead depends on the worker's judgment
\cite{chandler2013breaking,Finnerty2013}.  This includes such diverse tasks as
describing video and audio recordings, summarizing texts, or in clinical
diagnostic judgments.

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.8]{figs/theta.pdf}
	\caption{
		Empirical bias, $\theta_\mathrm{NB}$, measured using a na\"ive Bayes 
		classifier, induced in image labeling tasks, due to workers' 
		exposure to framing and initial tasks.  
		(\textbf{A}) Exposing workers to initial tasks induces more severe
		bias than framing, except when echoed framing is used. 
		(\textbf{B}) As workers proceed through test tasks, 
		the bias due to initial tasks wanes, 
		but remains significant even after five tasks.  
		Standard error bars are shown.
	}
	\label{fig:theta}
\end{figure}

@@

\begin{table*}
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{ c c c c c }

@@

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.87]{figs/vocab_specificity.pdf}
	\caption{
		Exposing workers to a priming concept, e.g. food, through
		initial tasks or framing, affects their tendency to focus
		on that concept, and the richness and specialization of their 
		vocaubulary in reference to it.
		In all three plots, positive values indicate a larger quantity for 
		the food-exposed workers.
		(\textbf{A}) Exposing workers to food does not necessarily increase
		the fraction food references they provide during test tasks.
		(\textbf{B}) The number of unique food-related
		words (richness) was greater for food-exposed workers, except in the 
		case of \textit{frame-food-culture} (stars indicate the threshold
		for a significant deviation, $\alpha=0.05$). 
		(\textbf{C}) Food-exposed
		workers used more specialized words to refer to food (see 
		supplementary text for calculation of relative specialization).
		Standard error bars are shown in (\textbf{A} and \textbf{C}).
	}
	\label{fig:specificity}
\end{figure}

@@

\section{Microtask setup} The work presented in the main text consisted of six
experiments involving HITs (bundles of tasks) performed on Amazon's Mechanical
Turk (MTurk) platform.  The flow of events experienced by a worker when
participating in this study is depicted in Fig.~S\ref{Sfig:task_schematic}.
Each experiment was divided into two treatments.  Treatments for a given
experiment differed with respect to a particular priming modality, which served
as the independent variable (as specified in Table~S\ref{Stable:experiments}).
The HITs for treatments of the same experiment always involved the same test
tasks (the last five tasks in the HIT), the results of which served as the
dependent variable.

>>>>

\usepackage{xr}
\externaldocument[S]{supp}
\usepackage{dcolumn}
\usepackage{booktabs}

@@

\dropcap{M}icrotask platforms are online marketplaces in which \textit{requesters} 
post batches of tasks, and \textit{workers} complete them
for remuneration, a sense of purpose, and fun
\cite{kazai2013analysis}.
Typical tasks include tagging and categorizing images,
%\cite{6116320,Zhai2012357}, 
coding and transcribing media,
%\cite{chandler2013breaking,Berinsky2012351,Finnerty2013},%paolacci2010running}, 
judging the relevancy or quality of content, 
and performing surveys for academic or market reserach purposes (see Table S\ref{Stable:task_composition} for a survey of task types).
%\cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.

@@

Our image-labeling tasks were performed on the MTurk microtask platform.  We
chose image labeling because it is very common,
%,paolacci2010running},
and because it is prototypical for tasks in which the worker is
asked to provide a response that is not precisely determined by the prompt, but
instead depends on the worker's judgment
\cite{chandler2013breaking,Finnerty2013}.  This includes such diverse tasks as
describing video and audio recordings, summarizing texts, or in clinical
diagnostic judgments.

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.8]{figs/theta.pdf}
	\caption{
		Empirical bias, $\theta_\mathrm{NB}$, measured using a na\"ive Bayes 
		classifier, induced in image labeling tasks, due to workers' 
		exposure to framing and initial tasks.  
		(\textbf{A}) Exposing workers to initial tasks induces more severe
		bias than framing, except when echoed framing is used. 
		(\textbf{B}) As workers proceed through test tasks, 
		the bias due to initial tasks wanes, 
		but remains significant even after five tasks.  
		Standard error bars are shown.
	\label{fig:theta}
	}
\end{figure}

@@

\begin{table*}[b]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{ c c c c c }

@@

\begin{figure}[t]
	\centering
	\includegraphics[scale=0.87]{figs/vocab_specificity.pdf}
	\caption{
		Exposing workers to a priming concept, e.g. food, through
		initial tasks or framing, affects their tendency to focus
		on that concept, and the richness and specialization of their 
		vocaubulary in reference to it.
		In all three plots, positive values indicate a larger quantity for 
		the food-exposed workers.
		(\textbf{A}) Exposing workers to food does not necessarily increase
		the fraction food references they provide during test tasks.
		(\textbf{B}) The number of unique food-related
		words (richness) was greater for food-exposed workers, except in the 
		case of \textit{frame-food-culture} (stars indicate the threshold
		for a significant deviation, $\alpha=0.05$). 
		(\textbf{C}) Food-exposed
		workers used more specialized words to refer to food (see 
		supplementary text for calculation of relative specialization).
		Standard error bars are shown in (\textbf{A} and \textbf{C}).
	}
	\label{fig:specificity}
\end{figure}

@@

\section{Microtask setup} This study involved six experiments involving HITs
(bundles of tasks) performed on Amazon's Mechanical Turk (MTurk) platform.  The
flow of events experienced by a worker when participating in this study is
depicted in Fig.~S\ref{Sfig:task_schematic}.  Each experiment was divided into
two treatments.  Treatments for a given experiment differed with respect to a
particular priming modality, which served as the independent variable (as
specified in Table~S\ref{Stable:experiments}).  The HITs for treatments of the
same experiment always involved the same test tasks (the last five tasks in the
HIT), the results of which served as the dependent variable.
